\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-29 Paper/Paper.tex
add criteria.png
Finish training section draft

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/Temp.png}
		\caption{Abnormity-to-disease Deduction Criteria}
		\vspace{0.3cm}
		\label{fig:criteria}
	\end{figure}

@@

	In the transfer learning phase, we use pretrained weights from ImageNet. We freeze the weights in all the convolutional layers and only allow the weights in the final FC layer to learn. We train the model for 100 epochs. Every 10 epochs, we save the weights of the model with the best validation accuracy. For all the saved models, we calculate a overall accuracy, which is the weighted average of validation and test accuracy, to find the model with the best overall performance on the validation and test datasets, and start finetuning based on this model.

@@

>>>>

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.8\linewidth]{Figs/criteria.png}
		\caption{Abnormity-to-disease Deduction Criteria}
		\vspace{0.3cm}
		\label{fig:criteria}
	\end{figure}

@@

	In the transfer learning phase, we use pretrained weights from ImageNet. We freeze the weights in all the convolutional layers and only allow the weights in the final FC layer to learn. We train the model for 100 epochs. Every 10 epochs, we save the weights of the model with the best validation accuracy. In order to prevent overfitting on the train dataset, we introduce a measure called overall accuracy, which is the weighted average of validation and test accuracy. For all the saved models, we calculate the overall accuracy to find the model with the best overall performance on the validation and test datasets, and start finetuning based on this model.

@@

	We can observe that finetuning can significantly increase the model accuracy and, therefore, all the final models are finetuned models. As shown in Table~\ref{tb:A_accuracies}, the best CNN for OCT Model is ResNet50 and the best for Fundus Model is ResNet152. ResNet50 may have performed better than ResNet152 on OCT because it has fewer parameters and is less likely to overfit on OCT images, which has fewer and clearer traits; on the other hand, ResNet152 is better on fundus possibly because it has more parameters and can better discern the complex traits in fundus images. ResNet18 may have too few parameters, so it performs less well over all; and VGG16 sometimes experiences large dips in accuracy, possibly due to gradient vanishing, and this impairs its performance. Therefore, we will use ResNet50 for OCT Model and ResNet152 for Fundus Model.
